A general Nullstellensatz for generalised spaces

### 2019-07-08 slides-edinburgh2019.tex
Final version of the slides

\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{stmaryrd}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{multicol}
\usepackage{tabto}
\usepackage{xstring}
\usepackage{ifthen}
\usepackage[normalem]{ulem}
\usepackage[all]{xy}
\xyoption{rotate}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,shapes.callouts,shapes.arrows,patterns,fit,backgrounds,decorations.pathmorphing,positioning}
\hypersetup{colorlinks=true}

@@

{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\hspace*{-1.7cm}\includegraphics[height=\paperheight,trim=0 0 16.9cm 0,clip]{black-hole-m87}\end{minipage}}
\begin{frame}[plain]
  \vspace*{\paperheight}\vspace*{-0.8cm}\scriptsize
  \centering
  \textcolor{white}{Fig.: The Event Horizon Telescope picture of the central black
  hole in the galaxy M87}
  \par

  \jnote{1}{At this meeting we had lots of discussions on the notion of space.
  Here is a picture of actual space, or rather the lack thereof, released only
  yesterday.}
\end{frame}}
\addtocounter{framenumber}{-1}

@@

  \textbf{Definition.} The \hil{syntactic site}~$\C_\TT$ has \ldots
  \begin{enumerate}
    \item objects: $\{ x_1\?X_1, \ldots, x_n\?X_n\_ \varphi \}$ (shorter:
    $\{ \vec x\_ \varphi \}$)
    \item morphisms: eqv. classes of \explainstub{provably functional
    formulas}{red!20}
    \item coverings: \explainstub{provably jointly surjective
    families}{purple!30}
  \end{enumerate}
  The topos of sheaves over~$\C_\TT$ is the \hil{classifying
  topos}~$\Set[\TT]$. The generic model interprets a sort~$X$ by~$\yon\{x\?X\_\top\}$.

@@

\begin{frame}{Working internally to toposes}
  \justifying
  Let~$\C$ be a site. We recursively define
  \[
    U \models \varphi \quad
    \text{(``$\varphi$ holds on~$U$'')}
  \]
  for objects~$U \in \C$ and \squiggly{formulas}~$\varphi$.
  Write~``$\Sh(\C) \models \varphi$'' for~$1 \models \varphi$.
  \footnotesize
  \[ \renewcommand{\arraystretch}{1.08}\begin{array}{@{}l@{\ \ }c@{\ \ }l@{}}
  U \models \top &\Ll& \text{true} \\
  U \models \bot &\Ll& \hcancel{\text{false}}{0pt}{3pt}{0pt}{-2pt}\ \text{the
  empty family is a covering of~$U$} \\
  U \models s = t \? F &\Ll& s|_U = t|_U \in F(U) \\
  U \models \varphi \wedge \psi &\Ll&
  \text{$U \models \varphi$ and $U \models \psi$} \\
  U \models \varphi \vee \psi &\Ll&
  \hcancel{\text{$U \models \varphi$ or $U \models
  \psi$}}{0pt}{3pt}{0pt}{-2pt}\ \text{there exists a covering $(U_i \to U)_i$} \\
  && \quad\quad\text{such that for all~$i$: $U_i \models \varphi$ or $U_i \models \psi$} \\
  U \models \varphi \Rightarrow \psi &\Ll&
  \text{for all~$V \to U$: }
  \text{$V \models \varphi$ implies $V \models \psi$} \\
  U \models \forall s \? F\_ \varphi(s) &\Ll&
  \text{for all $V \to U$ and sections~$s_0 \in F(V)$: $V \models \varphi(s_0)$} \\
  % U \models \forall F\_ \varphi(F) &\Ll&
  % \text{for all $V \to U$ and sheaves~$F_0$ over~$V$: $V \models \varphi(F_0)$} \\
  U \models \exists s \? F\_ \varphi(s) &\Ll&
  \hcancel{\text{there exists $s_0 \in F(U)$ such that $U \models \varphi(s_0)$}}{0pt}{3pt}{0pt}{-2pt} \\
  &&
  \text{there exists a covering $(U_i \to U)_i$ such that for all~$i$:} \\
  && \quad\quad \text{there exists~$s_0 \in F(U_i)$ such that $U_i \models \varphi(s_0)$}
  %U \models \exists F\_ \varphi(F) &\Ll&
  %\hcancel{\text{there exists a sheaf $F_0$ on $U$ such that $U \models
  %\varphi(F_0)$}}{0pt}{3pt}{0pt}{-2pt} \\
  %&&
  %\text{there exists a covering $(U_i \to U)_i$ such that for all~$i$:} \\
  %&& \quad\quad \text{there exists a sheaf~$F_0$ on $U_i$ such that $U_i \models \varphi(F_0)$}
  \end{array} \]

@@

\section{Affine schemes}

\begin{frame}{Affine schemes}
  \jnote{1}{
    A ring is \emph{local} iff every invertible sum contains an invertible
    summand, that is if~$1 \neq 0$ and if~$x + y$ invertible implies~$x$
    invertible or~$y$ invertible. Assuming the axiom of choice, this elementary
    definition is equivalent to the textbook definition of a local ring (a ring
    with exactly one maximal ideal). A ring homomorphism is \emph{local} iff it
    reflects invertibility.

    The notion of a \emph{filter} in a ring~$A$ is a direct axiomatisation of
    what classically would be the complement of a prime ideal. The filter
    axioms are: $1 \in F$, $(xy \in F) \Leftrightarrow ((x \in F) \wedge (y \in
    F))$, $\neg(0 \in F)$, $(x+y \in F) \Rightarrow ((x \in F) \vee (y \in F))$.

    A \emph{free local ring} over~$A$ is a homomorphism into a local
    ring~$A'$ such that any homomorphism into a local ring~$R$ factors uniquely
    over~$A'$ via a local homomorphism.

    For any particular local ring~$A \xrightarrow{f} R$, the
    localisation~$A[S^{-1}]$ with~$S = f^{-1}[R^\times]$ is a local ring which
    fits into the displayed diagram. However, in general there is no single
    choice of~$S$ which would work for any local ring~$R$. Indeed, classically
    one can show that a free local ring over~$A$ exists if and only if~$A$
    contains exactly one prime ideal, in which case~$A$ itself is the free
    local ring.
  }

  \jnote{2}{
    If we want a free local ring to exist for any ring~$A$, we have to broaden
    our notion of existence and embrace rings which live in toposes other
    than~$\Set$. There is a notion of a homomorphism between rings living in
    arbitrary toposes, and using this notion one can verify:

    The free local ring over~$A$ can be built in the classifying topos of
    filters of~$A$, as the localisation (in that topos) of~$A$ at the generic
    filter. (More precisely, as the localisation of the mirror image of~$A$ in that
    topos, that is the constant sheaf~$\underline{A}$.)

    The classifying topos of filters of~$A$ coincides with the topos of sheaves
    over what's called the \emph{spectrum of~$A$} in algebraic geometry, and
    under this equivalence the free local ring coincides with the structure
    sheaf of spectrum. In fact the classifying topos serves as a good
    constructive substitute for the classical spectrum construction,
    enjoying the expected universal property even if the axiom of choice is not
    available, which is why it is simply denoted~``$\Spec(A)$'' on the slide.

    (The classifying topos of prime ideals of~$A$ is also interesting; it
    coincides with the topos of sheaves over the spectrum of~$A$ equipped with
    the constructible topology.)
  }

  \jnote{3}{
    Assuming the Boolean prime ideal theorem, the geometric sequents
    validated by~$A^\sim$ are easy to describe: They are precisely those which
    are validated by all the stalks~$A_\ppp$ of~$A$.

    But~$A^\sim$ enjoys further unique properties which are not shared by the
    stalks of~$A$, other localisations of~$A$, quotients of~$A$ or indeed any
    reasonable construction. Three of these are displayed on the slide.
    (A ring is \emph{anonymously Noetherian} iff each of its ideals is
    \emph{not not} finitely generated. Textbook proofs of Hilbert's basis theorem
    are constructively acceptable for this Noetherian condition.)

    The object~$A^\sim$ strikes a fine balance: On the one hand, it is still
    close to~$A$, so that information learned about~$A^\sim$ teaches us
    about~$A$; on the other hand, it enjoys unique properties rendering it
    simpler than~$A$.

    This balance allows for a simple and conceptually satisfying proof of
    \emph{Gro\-then\-dieck's generic freeness lemma}, an important theorem in
    algebraic geometry. Details can be found in
    \fixedhref{https://rawgit.com/iblech/internal-methods/master/slides-padova2018.pdf}{this
    set of slides}.
  }

  Let~$A$ be a ring. Is there a \hil{free local ring}~$A \to A'$ over~$A$?
  \begin{columns}[t]
    \begin{column}{0.4\textwidth}
      $\xymatrix{
        A \ar[rd] \ar[rrr]^f &&& {\substack{\phantom{\text{local}}\\\text{\normalsize$R$}\\\text{local}}} \\
        & {\substack{\text{\normalsize$A'$}\\\text{local}}} \ar@{-->}_[@!35]{\text{local}}[rru]
      }$
    \end{column}

    \begin{column}{0.50\textwidth}
      \small\justifying
      For a fixed ring~$R$, the localisation $A' \defeq A[S^{-1}]$ with $S \defeq
      f^{-1}[R^\times]$ would do the job. ($S$ is a \emph{filter}.)
      \medskip

      Hence we need the \hil{generic filter}.
    \end{column}
  \end{columns}

  \justifying
  The free local ring over~$A$ is~$A^\sim \defeq \ul{A}[F^{-1}]$,
  where~$F$ is the generic filter, living in~$\Spec(A)$, the classifying topos
  of filters of~$A$.

  If~$A$ is reduced ($x^n = 0 \Rightarrow x = 0$):

  \vspace*{-0.8em}
  \setbeamercolor{block body}{bg=red!30}
  \setbeamercolor{structure}{fg=purple}
  \begin{varblock}{\textwidth}{}
    $A^\sim$ is a \hil{field}: $\forall x\?A^\sim\_ (\neg(\exists y\?A^\sim\_
    xy = 1) \Rightarrow x = 0)$.

@@

    \mbox{$A^\sim$ is \hil{anonymously Noetherian}.}\\[-1.2em]
  \end{varblock}
\end{frame}

@@

  \begin{quote}\emph{\mbox{For any \explainstub{geometric$^\star$ sequent~$\sigma$}{red!20} over
  the \explainstub{signature of~$\ul{\TT}/U_\TT$}{blue!20},}
  if~\explainstub{$\sigma$ holds for~$U_\TT$}{yellow!70}, then~\explainstub{$\ul{\TT}/U_\TT$
  proves~$\sigma$}{yellow!70}.}
  \end{quote}
  \vspace*{-0.6em}
}

@@

  \explainstub{\textbf{Definition.}}{blue!20} The theory~$\ul{\TT}/U_\TT$ is the
  internal geometric theory of~\hil{$U_\TT$-algebras}, the theory which arises from~$\ul{\TT}$ by adding:
  \begin{enumerate}
    \justifying\small
    \item for each element~$x : U_\TT$ a constant symbol~$e_x$,
    \item for each function symbol~$f$ and~$n$-tuple~$(x_1,\ldots,x_n) \in (U_\TT)^n$ the axiom
    $(\top \vdash f(e_{x_1},\ldots,e_{x_n}) = e_{f(x_1,\ldots,x_n)})$,
    \item for each relation symbol~$R$ and~$n$-tuple~$(x_1,\ldots,x_n) \in (U_\TT)^n$ such
    that~$R(x_1,\ldots,x_n)$ the axiom~$(\top \vdash R(e_{x_1},\ldots,e_{x_n}))$.
  \end{enumerate}

@@

\begin{frame}{Revisiting the test cases}
  \nullstellensatz
  \[ \xymatrix{
    & \text{$\ul{\TT}/U_\TT$ proves $\sigma$} \\
    \text{$\sigma$ holds for $U_\TT$} \ar@/^1.1pc/@{<=>}[ur] &&
    \text{$\sigma$ holds for $M$} \ar@/_1.1pc/@{<=}[ul]
  } \]

>>>>

\usepackage{graphbox}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{stmaryrd}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{multicol}
\usepackage{tabto}
\usepackage{xstring}
\usepackage{ifthen}
\usepackage[normalem]{ulem}
\usepackage[all]{xy}
\xyoption{rotate}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,shapes.callouts,shapes.arrows,patterns,fit,backgrounds,decorations.pathmorphing,positioning}
\hypersetup{colorlinks=true}

@@

{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\hspace*{-1.7cm}\includegraphics[height=\paperheight]{arthurs-seat-4}\end{minipage}}
\begin{frame}[plain]%
  \vspace*{\paperheight}\vspace*{-2.35cm}\hspace*{-1cm}%
  \includegraphics[width=\paperwidth/4]{arthurs-seat-7}%
  \includegraphics[width=\paperwidth/4]{arthurs-seat-0}%
  \includegraphics[width=\paperwidth/4]{arthurs-seat-5}%
  \includegraphics[width=\paperwidth/4]{arthurs-seat-9}%
\end{frame}}
\addtocounter{framenumber}{-1}

@@

  \textbf{Definition.} The \hil{syntactic site}~$\C_\TT$ has \ldots
  \begin{enumerate}
    \item objects: \explainstub{formulas-in-contexts}{red!20} $\{ x_1\?X_1, \ldots, x_n\?X_n\_ \varphi \}$
    \item morphisms: eqv. classes of \explainstub{provably functional
    formulas}{red!30}
    \item coverings: \explainstub{provably jointly surjective
    families}{purple!30}
  \end{enumerate}
  The topos of sheaves over~$\C_\TT$ is the \hil{classifying
  topos}~$\Set[\TT]$. The generic model interprets a sort~$X$ by the sheaf~$\yon\{x\?X\_\top\}$.

@@

\begin{frame}{Working internally to toposes}
  \justifying
  Let~$\C$ be a site. We recursively define
  \[
    U \models \varphi \quad
    \text{(``$\varphi$ holds on~$U$'')}
  \]
  for objects~$U \in \C$ and \squiggly{formulas}~$\varphi$.
  Write~``$\Sh(\C) \models \varphi$'' for~$U \models \varphi$ for all~$U$.
  \only<1>{\footnotesize
  \[ \renewcommand{\arraystretch}{1.08}\begin{array}{@{}l@{\ \ }c@{\ \ }l@{}}
  U \models \top &\Ll& \text{true} \\
  U \models \bot &\Ll& \hcancel{\text{false}}{0pt}{3pt}{0pt}{-2pt}\ \text{the
  empty family is a covering of~$U$} \\
  U \models s = t \? F &\Ll& s|_U = t|_U \in F(U) \\
  U \models \varphi \wedge \psi &\Ll&
  \text{$U \models \varphi$ and $U \models \psi$} \\
  U \models \varphi \vee \psi &\Ll&
  \hcancel{\text{$U \models \varphi$ or $U \models
  \psi$}}{0pt}{3pt}{0pt}{-2pt}\ \text{there exists a covering $(U_i \to U)_i$} \\
  && \quad\quad\text{such that for all~$i$: $U_i \models \varphi$ or $U_i \models \psi$} \\
  U \models \varphi \Rightarrow \psi &\Ll&
  \text{for all~$V \to U$: }
  \text{$V \models \varphi$ implies $V \models \psi$} \\
  U \models \forall s \? F\_ \varphi(s) &\Ll&
  \text{for all $V \to U$ and sections~$s_0 \in F(V)$: $V \models \varphi(s_0)$} \\
  % U \models \forall F\_ \varphi(F) &\Ll&
  % \text{for all $V \to U$ and sheaves~$F_0$ over~$V$: $V \models \varphi(F_0)$} \\
  U \models \exists s \? F\_ \varphi(s) &\Ll&
  \hcancel{\text{there exists $s_0 \in F(U)$ such that $U \models \varphi(s_0)$}}{0pt}{3pt}{0pt}{-2pt} \\
  &&
  \text{there exists a covering $(U_i \to U)_i$ such that for all~$i$:} \\
  && \quad\quad \text{there exists~$s_0 \in F(U_i)$ such that $U_i \models \varphi(s_0)$}
  %U \models \exists F\_ \varphi(F) &\Ll&
  %\hcancel{\text{there exists a sheaf $F_0$ on $U$ such that $U \models
  %\varphi(F_0)$}}{0pt}{3pt}{0pt}{-2pt} \\
  %&&
  %\text{there exists a covering $(U_i \to U)_i$ such that for all~$i$:} \\
  %&& \quad\quad \text{there exists a sheaf~$F_0$ on $U_i$ such that $U_i \models \varphi(F_0)$}
  \end{array} \]}

  \only<2>{
    \bigskip
    \begin{columns}[t]
      \begin{column}{0.45\textwidth}\justifying
        \textbf{Example.}
        $\Set \models \varphi$ if and only if $\varphi$ is true.
        \bigskip

        \textbf{Theorem.}
        If~$\Sh(\C) \models \varphi$ and if $\varphi$ intuitionistically
        entails~$\psi$, then also~$\Sh(\C) \models \psi$.
      \end{column}

      \begin{column}{0.45\textwidth}
        \includegraphics[width=\textwidth,align=t]{mike-shulman-stack-semantics}
        \vspace*{1.5em}
      \end{column}
    \end{columns}
  }

@@

\begin{frame}{A different kind of example}
  Let~$A$ be a reduced ring ($x^n = 0 \Rightarrow x = 0$).

  The \hil{generic local localisation}~$A^\sim$ of~$A$ validates:

  \vspace*{-1.8em}
  \setbeamercolor{block body}{bg=red!30}
  \setbeamercolor{structure}{fg=purple}
  \begin{varblock}{\textwidth}{}
    $A^\sim$ is a \hil{field}: $\forall x\?A^\sim\_ (\neg(\exists y\?A^\sim\_
    xy = 1) \Rightarrow x = 0)$.

@@

    \mbox{$A^\sim$ is \hil{anonymously Noetherian}.}\\[-1.2em]
  \end{varblock}

  Consequence: short and conceptual proof of Grothendieck's generic freeness
  lemma
\end{frame}

%\section{Affine schemes}
%
%\begin{frame}{Affine schemes}
%  \jnote{1}{
%    A ring is \emph{local} iff every invertible sum contains an invertible
%    summand, that is if~$1 \neq 0$ and if~$x + y$ invertible implies~$x$
%    invertible or~$y$ invertible. Assuming the axiom of choice, this elementary
%    definition is equivalent to the textbook definition of a local ring (a ring
%    with exactly one maximal ideal). A ring homomorphism is \emph{local} iff it
%    reflects invertibility.
%
%    The notion of a \emph{filter} in a ring~$A$ is a direct axiomatisation of
%    what classically would be the complement of a prime ideal. The filter
%    axioms are: $1 \in F$, $(xy \in F) \Leftrightarrow ((x \in F) \wedge (y \in
%    F))$, $\neg(0 \in F)$, $(x+y \in F) \Rightarrow ((x \in F) \vee (y \in F))$.
%
%    A \emph{free local ring} over~$A$ is a homomorphism into a local
%    ring~$A'$ such that any homomorphism into a local ring~$R$ factors uniquely
%    over~$A'$ via a local homomorphism.
%
%    For any particular local ring~$A \xrightarrow{f} R$, the
%    localisation~$A[S^{-1}]$ with~$S = f^{-1}[R^\times]$ is a local ring which
%    fits into the displayed diagram. However, in general there is no single
%    choice of~$S$ which would work for any local ring~$R$. Indeed, classically
%    one can show that a free local ring over~$A$ exists if and only if~$A$
%    contains exactly one prime ideal, in which case~$A$ itself is the free
%    local ring.
%  }
%
%  \jnote{2}{
%    If we want a free local ring to exist for any ring~$A$, we have to broaden
%    our notion of existence and embrace rings which live in toposes other
%    than~$\Set$. There is a notion of a homomorphism between rings living in
%    arbitrary toposes, and using this notion one can verify:
%
%    The free local ring over~$A$ can be built in the classifying topos of
%    filters of~$A$, as the localisation (in that topos) of~$A$ at the generic
%    filter. (More precisely, as the localisation of the mirror image of~$A$ in that
%    topos, that is the constant sheaf~$\underline{A}$.)
%
%    The classifying topos of filters of~$A$ coincides with the topos of sheaves
%    over what's called the \emph{spectrum of~$A$} in algebraic geometry, and
%    under this equivalence the free local ring coincides with the structure
%    sheaf of spectrum. In fact the classifying topos serves as a good
%    constructive substitute for the classical spectrum construction,
%    enjoying the expected universal property even if the axiom of choice is not
%    available, which is why it is simply denoted~``$\Spec(A)$'' on the slide.
%
%    (The classifying topos of prime ideals of~$A$ is also interesting; it
%    coincides with the topos of sheaves over the spectrum of~$A$ equipped with
%    the constructible topology.)
%  }
%
%  \jnote{3}{
%    Assuming the Boolean prime ideal theorem, the geometric sequents
%    validated by~$A^\sim$ are easy to describe: They are precisely those which
%    are validated by all the stalks~$A_\ppp$ of~$A$.
%
%    But~$A^\sim$ enjoys further unique properties which are not shared by the
%    stalks of~$A$, other localisations of~$A$, quotients of~$A$ or indeed any
%    reasonable construction. Three of these are displayed on the slide.
%    (A ring is \emph{anonymously Noetherian} iff each of its ideals is
%    \emph{not not} finitely generated. Textbook proofs of Hilbert's basis theorem
%    are constructively acceptable for this Noetherian condition.)
%
%    The object~$A^\sim$ strikes a fine balance: On the one hand, it is still
%    close to~$A$, so that information learned about~$A^\sim$ teaches us
%    about~$A$; on the other hand, it enjoys unique properties rendering it
%    simpler than~$A$.
%
%    This balance allows for a simple and conceptually satisfying proof of
%    \emph{Gro\-then\-dieck's generic freeness lemma}, an important theorem in
%    algebraic geometry. Details can be found in
%    \fixedhref{https://rawgit.com/iblech/internal-methods/master/slides-padova2018.pdf}{this
%    set of slides}.
%  }
%
%  Let~$A$ be a ring. Is there a \hil{free local ring}~$A \to A'$ over~$A$?
%  \begin{columns}[t]
%    \begin{column}{0.4\textwidth}
%      $\xymatrix{
%        A \ar[rd] \ar[rrr]^f &&& {\substack{\phantom{\text{local}}\\\text{\normalsize$R$}\\\text{local}}} \\
%        & {\substack{\text{\normalsize$A'$}\\\text{local}}} \ar@{-->}_[@!35]{\text{local}}[rru]
%      }$
%    \end{column}
%
%    \begin{column}{0.50\textwidth}
%      \small\justifying
%      For a fixed ring~$R$, the localisation $A' \defeq A[S^{-1}]$ with $S \defeq
%      f^{-1}[R^\times]$ would do the job. ($S$ is a \emph{filter}.)
%      \medskip
%
%      Hence we need the \hil{generic filter}.
%    \end{column}
%  \end{columns}
%
%  \pause
%
%  \justifying
%  The free local ring over~$A$ is~$A^\sim \defeq \ul{A}[F^{-1}]$,
%  where~$F$ is the generic filter, living in~$\Spec(A)$, the classifying topos
%  of filters of~$A$.
%
%  \pause
%
%  If~$A$ is reduced ($x^n = 0 \Rightarrow x = 0$):
%
%  \vspace*{-0.8em}
%  \setbeamercolor{block body}{bg=red!30}
%  \setbeamercolor{structure}{fg=purple}
%  \begin{varblock}{\textwidth}{}
%    $A^\sim$ is a \hil{field}: $\forall x\?A^\sim\_ (\neg(\exists y\?A^\sim\_
%    xy = 1) \Rightarrow x = 0)$.
%
%    $A^\sim$ has \hil{$\boldsymbol{\neg\neg}$-stable equality}:
%    $\forall x,y\?A^\sim\_ \neg\neg(x = y) \Rightarrow x = y$.
%
%    \mbox{$A^\sim$ is \hil{anonymously Noetherian}.}\\[-1.2em]
%  \end{varblock}
%\end{frame}

@@

  \vspace*{-0.3em}
  \begin{quote}\emph{\mbox{For any \explainstub{geometric$^\star$ sequent~$\sigma$}{red!20} over
  the \explainstub{signature of~$\ul{\TT}/U_\TT$}{blue!20},}
  if~\explainstub{$\sigma$ holds for~$U_\TT$}{yellow!70}, then~\explainstub{$\ul{\TT}/U_\TT$
  proves~$\sigma$}{yellow!70}.}
  \end{quote}
  \vspace*{-0.6em}
}

@@

  \explainstub{\textbf{Definition.}}{blue!20} The theory~$\ul{\TT}/U_\TT$ is the
  internal geometric theory of~\hil{$U_\TT$-algebras}, the theory which arises from~$\ul{\TT}$ by adding:
  \begin{enumerate}
    \justifying\small
    \item for each element~$x : U_\TT$ a constant symbol~$e_x$,
    \item for each function symbol~$f$ and~$n$-tuple~$(x_1,\ldots,x_n) : (U_\TT)^n$ the axiom
    $(\top \vdash f(e_{x_1},\ldots,e_{x_n}) = e_{f(x_1,\ldots,x_n)})$,
    \item for each relation symbol~$R$ and~$n$-tuple~$(x_1,\ldots,x_n) : (U_\TT)^n$ such
    that~$R(x_1,\ldots,x_n)$ the axiom~$(\top \vdash R(e_{x_1},\ldots,e_{x_n}))$.
  \end{enumerate}

@@

\begin{frame}{Revisiting the test cases}
  \nullstellensatz
  \vspace*{-2em}
  \[ \xymatrix{
    & \text{$\ul{\TT}/U_\TT$ proves $\sigma$} \\
    \text{$\sigma$ holds for $U_\TT$} \ar@/^1.1pc/@{<=>}[ur] &&
    \text{$\sigma$ holds for $M$} \ar@/_1.1pc/@{<=}[ul]
  } \]
